Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-03-06 Manuscript_plain_v3.tex
add acknowledgment

\section*{Acknowledgment}
We thank Linda Park for her foresight and perseverance, Katherine Maslenikov (University of Washington Burke Museum Ichthyology Collection) for providing tissue samples for the mock community analysis, and Olivia Scott for validation and Sanger sequencing of the mock communities. This material is based upon research supported by the Office of Naval Research under Award Number (N00014-22-1-2719). The authors gratefully acknowledge the survey expertise and support of NOAA NWFSC's Pacific hake survey team and the personnel of the NOAA Ship Bell M. Shimada for supporting the collection of eDNA samples on the west coast hake survey 2019 - 2023. Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.

>>>>

\section*{Acknowledgment}
We thank Linda Park for her foresight and perseverance, Katherine Maslenikov (University of Washington Burke Museum Ichthyology Collection) for providing tissue samples for the mock community analysis, and Olivia Scott for validation and Sanger sequencing of the mock communities. This material is based upon research supported by the Office of Naval Research under Award Number (N00014-22-1-2719) and support from the National Marine Fisheries Service's Genomic Strategic Initiative. The authors gratefully acknowledge the survey expertise and support of NOAA NWFSC's Pacific hake survey team and the personnel of the NOAA Ship Bell M. Shimada for supporting the collection of eDNA samples on the west coast hake survey 2019 - 2023. Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government.
